\documentclass[a4paper,10pt,dvipdfmx]{article}
\usepackage[left=2cm,right=2cm,top=2.2cm,bottom=2.2cm]{geometry}
\usepackage{xcolor}
\usepackage{indentfirst}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{enumitem}

\def\CC{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}}

\titleformat{\section}
{\normalfont\Large\bfseries}{\thesection}{0.5em}{}[\color{gray}\titlerule]

\begin{document}

\begin{center}
  {\huge \textbf{Yi-Chen Zhang}}
\end{center}

\section*{Contact Information}
\indent Address: 31350 Harlo Dr Apt H, Madison Heights, MI 48071\\
\indent Phone: 517-775-9919\\
\indent E-mail: chris7462@gmail.com\\
\indent Website: \href{https://chris7462.github.io}{https://chris7462.github.io}

\section*{Education}
\indent \textbf{Ph.D., Department of Statistics and Probability} \hfill Aug.~2013 -- Jun.~2018\\
\indent Michigan State University, East Lansing, MI\\
\indent Advisor: \href{https://www.stt.msu.edu/users/luda/}{Dr. Lyudmila Sakhanenko}\\
\indent Dissertation: Functional Data Analysis with Application to Traffic Flow Data\\

\indent \textbf{M.S., Graduate Institute of Statistics} \hfill Sep.~2007 -- Jun.~2009\\
\indent National Central University, Taiwan\\
\indent Advisor: \href{http://www.stat.ncu.edu.tw/teacher/THFan/index.htm}{Dr. Tsai-Hung Fan}\\
\indent Thesis: Bayesian Model Selection in Linear Mixed Effects Models with AR$(1)$ Errors\\

\indent \textbf{B.S., Department of Mathematics} \hfill Sep.~2003 -- Jun.~2007\\
\indent National Central University, Taiwan

\section*{Work Experience}
\textbf{Isuzu -- Technical Center of America, Inc.~(ITCA)} \hfill Jan.~2021 -- Present
\begin{itemize}[noitemsep,nolistsep]
  \item[] Sr.~Engineer, Autonomous and Artificial Intelligence -- Advanced Engineering \hfill Jan.~2022 -- Present
    \begin{itemize}[noitemsep,nolistsep]
      \item Acting scrum master of the autonomous driving team.
      \item Make key contributions to the software architecture design and software stack integration.
      \item Lead the development of perception and visualization
      \item[] Implementation ROS visualization for MVXNet using Kitti dataset: \href{https://www.youtube.com/watch?v=LQHUm6AnVdg}{MVXNet demo}.
      \item[] Develop structure aware single-stage 3D objection detection.
      \item Develop localization component including: wheel odometry, GNSS/IMU processing,
      \item[] and Fast-LOAM. These outputs are later fused in the Robot Localization package.
      \item Provide technical support and career growth direction for team members.
      \item Supervised four interns who worked across sub-modules of AD software stack.
    \end{itemize}
  \item[] Autonomous Driving Engineer -- PVRD Team \hfill Jan.~2021 -- Present
    \begin{itemize}[noitemsep,nolistsep]
      \item Develop core sensor component for centralized sensor fusion for both cameras and LiDARs.
      %\item Lead the perception, localization, mapping, and planning team. 	
      %\item Define team's furture direction and lead the technology roadmap. 	
      \item Curb detection using 3D LiDAR point clouds: \href{https://chris7462.github.io/Demo/moriyama.mp4}{Moriyama dataset demo}.
      \item Object detection using 3D LiDAR point clouds: \href{https://chris7462.github.io/Demo/lidar_eculidean_cluster_detection.mp4}{Moriyama dataset demo}.
      \item Point clouds 3D map construction using Fast LOAM and OctoMap: \href{https://chris7462.github.io/Demo/3D_map_resolution_0.2.mp4}{Moriyama dataset demo}.
      \item Software stack management with release tags and version control by git submodules.
      \item Component integration and testing in both simulation and on the truck.\\
    \end{itemize}
\end{itemize}

\textbf{Aptiv -- Global Technology Company} \hfill Jul.~2018 -- Jan.~2021
\begin{itemize}[noitemsep,nolistsep]
	\item[] Algorithm Engineer -- Scene Perception Algorithm Team \hfill Oct.~2020 -- Jan.~2021
    \begin{itemize}[noitemsep,nolistsep]
      \item Mainly develop unit test cases in vectorCAST for different components.
    \end{itemize}
  \item[] Algorithm Engineer - Fused Road Model (FRM) Team \hfill Sep.~2018 -- Sep.~2020
    \begin{itemize}[noitemsep,nolistsep]
      \item Develop fusion algorithms for object trail processing:\\
        NGSIM dataset demo for \href{https://chris7462.github.io/Demo/road_shape_estimation.mp4}{road shape estimation} and \href{https://chris7462.github.io/Demo/lane_centerlines_prediction.mp4}{lane centerline prediction}.
      %\item Fused track converter for ROS, Appsil, and AUTOSAR Adaptive variants.
      \item Design FRM state machine and mode manager.
      \item Error handling for vision, object fusion, and vehicle state inputs.
      \item Maintain input Rosbag pipeline.
      \item Develop FRM analysis pipeline and dashboard.
      \item Coverity Static Analysis including AUTOSAR and MISRA \CC.
      \item Develop unit test cases in Google Test and component test for FRM component.
      %\item Follow the global SPICE compliant process (GSCP).
      \item Sporadically acted as the scrum master for FRM.
    \end{itemize}
  \item[] Algorithm Engineer - Autonomous Driving Behavior Team \hfill Jul.~2018 -- Aug.~2018
    \begin{itemize}[noitemsep,nolistsep]
      \item Develop a prediction and cost function based algorithm to perform cooperative social behavior.
      \item Work in Ottomatika code migration from urban pilot to highway pilot.
      \item Sporadically give numerical methods of statistical lectures.\\
    \end{itemize}
\end{itemize}

\textbf{Michigan State University} \hfill Aug.~2013 -- May.~2018
\begin{itemize}[noitemsep,nolistsep]
  \item[] Teaching Assistant -- Department of Statistics and Probability \hfill Jan.~2017 -- May.~2018
    \begin{itemize}[noitemsep,nolistsep]
      \item One semester of a graduate-level of Statistics class.
      \item One semester of senior-level of Probability and Statistics for Business classes.
      \item Two semesters of entry-level of Statistics classes.
    \end{itemize}
  \item[] Research Assistant -- Computational Mathematics Science and Engineering \hfill Jan.~2016 -- Dec.~2016
    \begin{itemize}[noitemsep,nolistsep]
      \item[] \hspace{-3ex} Supervisor: \href{https://cmse.msu.edu/directory/faculty/yuying-xie/}{Dr.~Yuying Xie} and \href{https://msu.edu/~reimersm/}{Dr.~Mark Reimers}.
      \item Research in neuroimaging data for brain activity.
      \item Movement correction, denosing, and registration for images.
      \item Analyze the amplitude and phase for images by Fourier analysis.
    \end{itemize}
  \item[] Teaching Assistant -- Department of Statistics and Probability \hfill Aug.~2013 -- Dec.~2015
    \begin{itemize}[noitemsep,nolistsep]
      \item Summer instructor of an entry-level Statistics class.
      \item One semester of graduate-level of Statistics classes.
      \item Three semesters of senior-level of Probability and Statistics classes.\\
    \end{itemize}
\end{itemize}

\textbf{Academia Sinica} \hfill Aug.~2010 -- Jul.~2013
\begin{itemize}[noitemsep,nolistsep]
  \item[] Research Assistant -- Institute of Statistical Science
    \begin{itemize}[noitemsep,nolistsep]
      \item[] \hspace{-3ex} Supervisor: \href{http://www.stat.sinica.edu.tw/jmchiou/}{Dr.~Jeng-Min Chiou}.
      \item Mainly research in functional data.
      \item Functional clustering and classification.
      \item Functional linear model and its prediction and applications.
      \item Missing value imputation and outlier detection for functional data.
      \item Programming assistant \href{https://projecteuclid.org/euclid.aoas/1356629052/}{(Chiou, J.-M., Annals of Applied Statistics, 2012)}.\\
    \end{itemize}
\end{itemize}

\textbf{Military Service, Taiwan} \hfill Aug.~2009 -- Aug.~2010
\begin{itemize}[noitemsep,nolistsep]
  \item[] Corporal -- Beigan Township, Lienchiang County
    \begin{itemize}[noitemsep,nolistsep]
      \item The duties include training, safety, and communications.\\
    \end{itemize}
\end{itemize}

\textbf{National Central University} \hfill Feb.~2004 -- Jun.~2009
\begin{itemize}[noitemsep,nolistsep]
  \item[] Network Administrator -- Graduate Institute of Statistics \hfill Jul.~2007 -- Jun.~2009
    \begin{itemize}[noitemsep,nolistsep]
      \item Manage and maintain the e-mail server based on FreeBSD operating system.
      \item Design an alumni website for graduate alumnus.
      \item Maintenance and elimination of common breakdown of the PCs in computer laboratory.
    \end{itemize}
  \item[] Network Administrator -- Mathematics Computation Laboratory \hfill Feb.~2005 -- Jun.~2007
    \begin{itemize}[noitemsep,nolistsep]
      \item Manage the e-mail server and design some rules to block spam mails.
      \item Design a network sync upgrade system of more than 80 computers over 2 classrooms.
      \item Devise a web-based roll call and sign-in system.
    \end{itemize}
  \item[] Network Assistant -- Mathematics Computation Laboratory \hfill Feb.~2004 -- Jan.~2005
    \begin{itemize}[noitemsep,nolistsep]
      \item Provide software supports and computer consulting for freshmen.
      \item Supervise the networking, system analysis, and trouble shooting.
    \end{itemize}
\end{itemize}

\section*{Teaching Experience}
\begin{small}
  \begin{tabular}{llll}
    Year  & Semester& Role       & Course number with title\\
    2018  & Spring  & TA         & STT 231 Statistics for Scientists\\
    2017  & Fall	  & TA				 & STT 200 Statistical Methods\\
          &			    & GA				 & STT 873 Statistical Learning and Data Mining\\
          & Spring  & TA				 & STT 315 Introduction to Probability and Statistics for Business\\
    2016  & Fall    & RA$^{*}$   & STT 442 Probability and Statistics II: Statistics\\
          &         &            & STT 861 Theory of Probability and Statistics I\\
    2015  & Fall	  & TA				 & STT 200 Statistical Methods\\
          & Summer  & Instructor & STT 200 Statistical Methods\\
          & Spring  & TA				 & STT 224 Introduction to Probability and Statistics for Ecologists\\
    2014  & Fall	  & GA				 & STT 863 Statistical Methods I\\
          &			    &						 & STT 886 Stochastic Processes and Applications\\
          & Summer  & GA				 & STT 421 Statistics I\\
          &			    &						 & STT 430 Introduction to Probability and Statistics\\
          & Spring  & GA				 & STT 351 Probability and Statistics for Engineering\\
          &			    &						 & STT 430 Introduction to Probability and Statistics\\
    2013  & Fall	  & GA				 & STT 441 Probability and Statistics I: Probability\\
    \multicolumn{4}{l}{$*$: Sporadically acted as teaching substitute.}
  \end{tabular}
\end{small}

\section*{Publications}
\begin{itemize}[noitemsep,nolistsep]
  %\item[1.] \textbf{Zhang, Y.-C.} (2020+). \textit{Dynamical Highway Vehicle Lane Classification Using Vehicle Trails}. (In preparation)
  \item[1.] Zhang, W., Yu, W., Jia, Q., and \textbf{Zhang, Y.-C.} (2022) \textit{Exploration and Sweeping for Autonomous Sweeper Truck}. Isuzu Technical Journal \textbf{134}, 42-51.
  \item[2.] \textbf{Zhang, Y.-C.} (2021) \href{https://www.tandfonline.com/doi/full/10.1080/15472450.2021.1974858}{\textit{Road Geometry Estimation Using Vehicle Trails: A Linear Mixed Model Approach}}. Journal of Intelligent Transportation Systems.
  \item[3.] \textbf{Zhang, Y.-C.} and Sakhanenko, L. (2019) \href{https://www.sciencedirect.com/science/article/pii/S0167715219301208}{\textit{The Naive Bayes Classifier for Functional Data}}. Statistics \& Probability Letter \textbf{152}, 137-146.
  \item[4.] Chiou, J.-M., \textbf{Zhang, Y.-C.}, Chen, W.-H., and Chang, C.-W. (2014) \href{http://www.tandfonline.com/doi/abs/10.1080/21680566.2014.892847}{\textit{A Functional Data Approach to Missing Value Imputation and Outlier Detection for Traffic Flow Rate Data}}. Transportmetrica B: Transport Dynamics \textbf{2}, 106-129.
  \item[5.] Fan, T.-H., Wang, Y.-F., and \textbf{Zhang, Y.-C.} (2014) \href{http://www.tandfonline.com/doi/abs/10.1080/02664763.2014.894001?journalCode=cjas20}{\textit{Bayesian Model Selection in Linear Mixed Effects Models with AR(1) Errors Using Mixture Priors}}. Journal of Applied Statistics \textbf{41}, 1814-1829.
\end{itemize}

\section*{Referee Service}
\begin{itemize}[noitemsep,nolistsep]
  \item \href{https://chris7462.github.io/BIOM_Reviewer_Certificate.pdf}{Biometrics}.
\end{itemize}

\section*{Honors/Awards}
\begin{itemize}[noitemsep,nolistsep]
  \item College of Natural Science Dissertation Continuation Fellowship Summer 2017, Michigan State University.
  \item College of Natural Science Dissertation Completion Fellowship Summer 2018, Michigan State University.
\end{itemize}

\section*{Computer Skills}
\begin{itemize}[noitemsep,nolistsep]
  \item Advanced knowledge in \CC.
  \item Experienced in using mathematics and statistics software including \textsf{MATLAB} and \textsf{R}.
  % \item Experienced in using \textsf{C}\texttt{++} and Python
  \item Ability to use \CC~under \textsf{R} and \textsf{MATLAB} to carry out secondary development.
  % \item Ability to use \textsf{C}\texttt{++} under \textsf{R} and \textsf{MATLAB} to carry out secondary development
  \item Extensive experience of using Linux system with a focus on Ubuntu.
  \item Strong knowledge of Linux/Unix environment and commends.
  %\item Knowledgeable to write shell scripts such as Perl to automate tasks.
  \item Understanding and experience to work with parallel computing API such as openMP and MPI.
  \item Experience with high performance cluster computer (HPCC) such as Torque and SLURM.
  \item Proficient in \LaTeX~for document preparation and Ti\textit{k}Z for producing vector graphics.
  \item Fluent with version control tools such as git (gitlab and gerrit), Subversion (SVN), and Plastic SCM.
  %\item Working knowledge of structure query language such as MySQL.
  \item Working knowledge of Robot Operating System (ROS).
  \item Having experience on static analysis including AUTOSAR, MISRA, and CERT \CC~coding standard.
  \item Experienced in unit test including google test and vectorCAST.
  \item Working knowledge of OpenCV and PCL.
\end{itemize}

\section*{Software Packages}
\begin{itemize}[noitemsep,nolistsep]
  \item \href{https://github.com/Chris7462/Autologistic-Models}{\textbf{Autologistic-Models}}: An \textsf{R} package implemented in \CC. The objective of this program is to reduce the estimating bias of parameters when fitting autologistic models.
  \item \href{https://github.com/Chris7462/Modified-Rainbow}{\textbf{Modified-Rainbow}}: A modified version of rainbow package in \textsf{R} that uses the functional principal component instead of the robust principal component.
  \item \href{https://github.com/Chris7462/Parallel-Kernel}{\textbf{Parallel-Kernel}}: The kernel density estimation implemented in \CC~and paralleled via OpenMP.
  \item \href{https://github.com/Chris7462/Monte-Carlo-EM-Algorithm}{\textbf{MCEM}}: An \textsf{R} function with Mwanza example that realizes the method proposed by \href{https://www.jstor.org/stable/1391097}{Richard A.~Levine and George Casella (2001)}.
\end{itemize}

\section*{Documents}
\begin{itemize}[noitemsep,nolistsep]
  \item \textbf{Ti\textit{k}Z}: A tutorial document about how to use basic Ti\textit{k}Z commends. See \href{https://github.com/Chris7462/TikZ/blob/master/TikZ_basic.pdf}{TikZ basic} and \href{https://github.com/Chris7462/TikZ/blob/master/Examples/Doraemon.pdf}{Doraemon}.
\end{itemize}

\end{document}
