\documentclass[11pt]{article}

\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{setspace}

\setstretch{1.05}
\pagenumbering{gobble}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{6pt}

\begin{document}

\begin{center}
    {\LARGE \textbf{Yi-Chen Zhang, Ph.D.}} \\
    Research Software Engineer – Autonomous Perception \\
    \vspace{4pt}
    517-775-9919 \quad
    \href{mailto:chris7462@gmail.com}{chris7462@gmail.com} \quad
    \href{https://github.com/Chris7462}{github.com/Chris7462} \quad
    \href{https://www.linkedin.com/in/yi-chen-zhang-b72907116/}{LinkedIn}
\end{center}

%=================================================
\section*{Professional Summary}

Hands-on Research Software Engineer with 8+ years of experience in autonomous driving perception, combining deep learning research, statistical modeling, and high-performance C++ implementation.

Ph.D.-trained in Statistics with strong foundation in probabilistic modeling, Bayesian inference, and matrix Lie group methods for state estimation. Experienced in developing and evaluating new perception algorithms (object detection, tracking, SLAM) and translating research prototypes into efficient, real-time automotive systems using PyTorch, CUDA, and TensorRT.

Bridges research innovation and production-grade software engineering.

%=================================================
\section*{Core Competencies}

\textbf{Perception Research}
\begin{itemize}[leftmargin=*]
\item 2D/3D Object Detection (FCOS, LiDAR detection, MVXNet)
\item Multi-object Tracking (SORT, 3D LiDAR MOT)
\item Visual SLAM, Fast-LOAM, OctoMap
\item Investigation of transformer-based perception architectures
\item Model evaluation, ablation studies, and performance benchmarking
\end{itemize}

\textbf{Statistical Modeling \& State Estimation}
\begin{itemize}[leftmargin=*]
\item Bayesian inference and uncertainty modeling
\item Error-State Kalman Filter on Matrix Lie Groups
\item GNSS/IMU fusion and probabilistic localization
\item Linear mixed models and functional data analysis
\end{itemize}

\textbf{Software Engineering \& Deployment}
\begin{itemize}[leftmargin=*]
\item C++ (advanced), Python (advanced)
\item PyTorch model development and ONNX export
\item TensorRT engine build and CUDA-accelerated inference
\item Latency profiling and backbone/post-processing optimization
\item ROS 2 package development and system integration
\item AUTOSAR/MISRA compliance and static analysis (Coverity)
\end{itemize}

%=================================================
\section*{Professional Experience}

\textbf{Isuzu Technical Center of America (ITCA)} \hfill 2021--Present

\textit{Lead Engineer – Autonomous \& Artificial Intelligence (2024--Present)}
\begin{itemize}[leftmargin=*]
\item Conduct research on perception algorithms for autonomous driving, including object detection, tracking, and localization.
\item Investigate transformer-based architectures and manifold-based state estimation methods for next-generation perception systems.
\item Develop C++ inference backends using NVIDIA TensorRT, reducing FCOS detection latency from 591 ms (PyTorch CUDA) to 34 ms (TensorRT), achieving real-time performance (~29 FPS).
\item Design modular evaluation pipelines for systematic benchmarking and latency regression testing.
\item Build and maintain SLURM-based GPU compute environment supporting large-scale perception experiments.
\end{itemize}

\textit{Senior Engineer – Autonomous \& Artificial Intelligence (2022--2024)}
\begin{itemize}[leftmargin=*]
\item Developed 3D LiDAR object detection and multi-object tracking algorithms for autonomous vehicle platform.
\item Implemented GNSS/IMU fusion, wheel odometry, and Visual SLAM for vehicle localization.
\item Integrated perception modules within ROS 2-based autonomous stack and conducted on-vehicle validation.
\item Mentored junior engineers and supervised research-oriented development projects.
\end{itemize}

\textit{Autonomous Driving Engineer (2021)}
\begin{itemize}[leftmargin=*]
\item Developed sensor fusion components (camera + LiDAR) for centralized perception system.
\item Implemented curb detection and 3D map construction using Fast-LOAM and OctoMap.
\item Conducted simulation and real-vehicle integration testing.
\end{itemize}

\vspace{6pt}

\textbf{APTIV} \hfill 2018--2021

\textit{Algorithm Engineer – Scene Perception \& Fused Road Model}
\begin{itemize}[leftmargin=*]
\item Designed and implemented road geometry estimation and lane centerline prediction algorithms.
\item Developed FRM state machine and robust error-handling mechanisms across perception inputs.
\item Ensured AUTOSAR/MISRA compliance and implemented unit tests (Google Test, VectorCAST).
\item Built analysis pipelines and dashboards for perception performance evaluation.
\end{itemize}

%=================================================
\section*{Selected Research \& Technical Contributions}

\begin{itemize}[leftmargin=*]
\item Developed Error-State Kalman Filter on Matrix Lie Groups for improved vehicle pose consistency (preprint).
\item Reduced semantic segmentation inference latency from 406 ms to 26 ms (15$\times$ speedup) using TensorRT backend.
\item Designed benchmark suites for quantitative evaluation of inference performance (avg/min/max latency).
\item Published research in statistical modeling and transportation systems journals.
\end{itemize}

%=================================================
\section*{Publications}

\begin{itemize}[leftmargin=*]
\item Zhang, Y.-C. (2025+) Error State Kalman Filter on Matrix Lie Group (preprint).
\item Zhang et al. (2022) Exploration and Sweeping for Autonomous Sweeper Truck. \textit{Isuzu Technical Journal}.
\item Zhang, Y.-C. (2021) Road Geometry Estimation Using Vehicle Trails. \textit{Journal of Intelligent Transportation Systems}.
\item Zhang, Y.-C. and Sakhanenko (2019) Naive Bayes Classifier for Functional Data. \textit{Statistics \& Probability Letters}.
\end{itemize}

%=================================================
\section*{Education}

\textbf{Ph.D., Statistics} \hfill Michigan State University \\
Dissertation: Functional Data Analysis with Applications to Traffic Flow

\textbf{M.S., Statistics} \hfill National Central University

\textbf{B.S., Mathematics} \hfill National Central University

\end{document}
